---
title: "RDeep HeLa Interphase Analysis"
author: "Laura Herrfurth"
date: "8 5 2022"
output: html_document
---

```{r}
#Load data RDeep_HeLa_Interphase 
FullDat <- read.table("C:/Users/Laura Herrfurth/Documents/Data Analysis Projekt/RDeeP_HeLa_Interphase.csv", header = TRUE, row.names=1, sep = ";") 

save(FullDat, file = "FullDat.Rdata")
load("FullDat.Rdata")

#First survey
head(FullDat)
summary(FullDat)
dim(FullDat)
colnames(FullDat)
rownames(FullDat)

sapply(FullDat,mode)
sapply(FullDat,class)



```

The data contains 7086 proteins and 25 fractions which were each repeated three times as a control sample and three times with RNase.

After the first survey we have to find a way to deal with the missing values in the data.The options are to remove rows (proteins) with a very high count or to replace all missing values with the mean of the general count of a specific protein of the control or the RNase sample. We will delete row with all zeros and with all zeros in either all Ctrl replicates or in all RNase replicates.


```{r}



#Reduce data set into smaller data sets 
colRep1ctrl = seq(1, 150, 6) ##all columns with rep1 ctrl 
colRep2ctrl = seq(2, 150, 6) ##all columns with rep2 ctrl 
colRep3ctrl = seq(3, 150, 6) ##all columns with rep3 ctrl 

colRep1rnase = seq(4, 150, 6) ##all columns with rep1 RNase 
colRep2rnase = seq(5, 150, 6) ##all columns with rep2 RNase 
colRep3rnase = seq(6, 150, 6) ##all columns with rep3 RNase 

# delete rows with only zeros or proteins with only zeros in the Ctrl or RNase samples
a = which(rowSums(FullDat==0)==150)
b = which(rowSums(FullDat[,c(colRep1ctrl, colRep2ctrl, colRep3ctrl)]== 0) ==75)
c = which(rowSums(FullDat[,c(colRep1RNAse, colRep2RNAse, colRep3RNAse)]== 0) ==75)


FullDat = FullDat[-c(2089,2993, 4123,4405, 6216),]

```
Now that we have a survey about our data and performed a first data reduction we will normalize the data.

```{r}

# data sets for each replicate; normalization, row-wise
rep1ctrlnormData = t(apply(FullDat[, colRep1ctrl], 1, function(x) x/(sum(x)/100)))
rep2ctrlnormData = t(apply(FullDat[, colRep2ctrl], 1, function(x) x/(sum(x)/100)))
rep3ctrlnormData = t(apply(FullDat[, colRep3ctrl], 1, function(x) x/(sum(x)/100)))
rep1rnasenormData = t(apply(FullDat[, colRep1rnase], 1, function(x) x/(sum(x)/100)))
rep2rnasenormData = t(apply(FullDat[, colRep2rnase], 1, function(x) x/(sum(x)/100)))
rep3rnasenormData = t(apply(FullDat[, colRep3rnase], 1, function(x) x/(sum(x)/100)))

#Transformation into dataframes
rep1ctrlnormDataframe = as.data.frame(rep1ctrlnormData)
rep2ctrlnormDataframe = as.data.frame(rep2ctrlnormData)
rep3ctrlnormDataframe = as.data.frame(rep3ctrlnormData)
rep1rnasenormDataframe = as.data.frame(rep1rnasenormData)
rep2rnasenormDataframe = as.data.frame(rep2rnasenormData)
rep3rnasenormDataframe = as.data.frame(rep3rnasenormData)

sum(rep1ctrlnormData[1,]) # == 100



# normalization fraction-wise

FullDat[is.na(FullDat)] = 0
rep_sum = apply(FullDat, 2, sum)

#Ctrl sum fraction-wise before normalization
for (i in colRep1ctrl){
  barplot(rep_sum[i:(i+2)])}

#RNase sum fraction-wise before normalization
for (i in colRep1rnase){
  barplot(rep_sum[i:(i+2)])
}

#vector with mean for each fraction, each condition and each replicate (= 150 values)
mean_frac_rep = apply(FullDat, 2, mean)

#normalization fraction-wise/ column-wise
col_frac_per_condition = sort(c(colRep1ctrl, colRep1rnase))
##vector with mean value of two mean values that are closest to each other in each fraction of each condition (comparing mean values of triplicates):
mean_rep = vector() 
for (i in 1:50){
  a = mean_frac_rep[col_frac_per_condition[i]]
  b = mean_frac_rep[col_frac_per_condition[i]+1]
  c = mean_frac_rep[col_frac_per_condition[i]+2]
  if(abs(a-b) <= abs(b-c) && abs(a-b) <= abs(a-c)){ mean_rep[i] = mean(c(a,b))}
    else if(abs(b-c) < abs(a-b) && abs(b-c) <= abs(a-c)){mean_rep[i] = mean(c(b,c))}
      else{mean_rep[i] = mean(c(a,c))}
}

#normalization to mean values stored in mean_rep
FullDat_fracnorm = data.frame(FullDat)
for (i in 1:50) {
  for (j in col_frac_per_condition[i]:(col_frac_per_condition[i]+2)){
    x = mean_rep[i]/mean_frac_rep[j]
    FullDat_fracnorm[,j] = FullDat[,j]*x
    
  }
} 


#testing if all fraction-wise sums/means are equal after normalization

rep_sum_norm = apply(FullDat_fracnorm, 2, sum)
#Ctrl sum fraction-wise before normalization
for (i in colRep1ctrl){
  barplot(rep_sum_norm[i:(i+2)])}

#RNase sum fraction-wise before normalization
for (i in colRep1rnase){
  barplot(rep_sum_norm[i:(i+2)])
}

rep_mean_norm = apply(FullDat_fracnorm, 2, mean)
for (i in colRep1ctrl){
  barplot(rep_mean_norm[i:(i+2)])}

for (i in colRep1rnase) {
  barplot(rep_mean_norm[i:(i+2)])
}


## data sets for each replicate; normalization, row-wise
rep1ctrlnormData = t(apply(FullDat_fracnorm[, colRep1ctrl], 1, function(x) x/(sum(x)/100)))
rep2ctrlnormData = t(apply(FullDat_fracnorm[, colRep2ctrl], 1, function(x) x/(sum(x)/100)))
rep3ctrlnormData = t(apply(FullDat_fracnorm[, colRep3ctrl], 1, function(x) x/(sum(x)/100)))
rep1rnasenormData = t(apply(FullDat_fracnorm[, colRep1rnase], 1, function(x) x/(sum(x)/100)))
rep2rnasenormData = t(apply(FullDat_fracnorm[, colRep2rnase], 1, function(x) x/(sum(x)/100)))
rep3rnasenormData = t(apply(FullDat_fracnorm[, colRep3rnase], 1, function(x) x/(sum(x)/100)))#

#Transformation into dataframes
rep1ctrlnormDataframe = as.data.frame(rep1ctrlnormData)
rep2ctrlnormDataframe = as.data.frame(rep2ctrlnormData)
rep3ctrlnormDataframe = as.data.frame(rep3ctrlnormData)
rep1rnasenormDataframe = as.data.frame(rep1rnasenormData)
rep2rnasenormDataframe = as.data.frame(rep2rnasenormData)
rep3rnasenormDataframe = as.data.frame(rep3rnasenormData)
```
We normalized our data in two different ways. First we normalized the protein amount of each replicate of each Ctrl and RNase to 100 (row-wise) to be able to compare the three replicates. After that we normalized the protein amount of each of the three replicates of the two groups fraction-wise, so that there is the same amount of protein in each replicate.

```{r}



#mean of control replicates of all proteins  
meanRepctrl = matrix(nrow= nrow(FullDat), ncol = 25)
for (j in 1:nrow(FullDat)){ 
  for (i in 1:25){
    meanRepctrl[j,i] = (rep1ctrlnormDataframe[j,i] + rep2ctrlnormDataframe[j,i] + rep3ctrlnormDataframe[j,i])/3}}
meanRepctrl = as.data.frame(meanRepctrl, colnames = c(1:25), rownames = rownames(FullDat))

#mean of RNase replicates of all proteins 
meanRepRNase = matrix(nrow= nrow(FullDat), ncol = 25)
for (j in 1:nrow(FullDat)){ 
  for (i in 1:25){
    meanRepRNase[j,i] = (rep1rnasenormDataframe[j,i] + rep2rnasenormDataframe[j,i] + rep3rnasenormDataframe[j,i])/3}}
meanRepRNase = as.data.frame(meanRepRNase, colnames = c(1:25), rownames = rownames(FullDat))


```
After deleting proteins we have to examine differences in the different samples and to illustrate them. That's why we normalized our data to compare the different replicates.We normalized the amount of one replicate to 100 to be able to assign protein amounts to percentages/relations. We are looking at the plots of single proteins and compare the lines and maxima of the control and the RNase group. 

```{r}
#Plots for fractions of each gene
#not normalized
y=1:25

for (i in 4200:4300){
plot(y, FullDat[i,colRep1ctrl], col = "blue", xlab = i) ##plot of Rep1 ctrl sample for some proteins
lines(y, FullDat[i,colRep2ctrl], col = "blue") ##plot of Rep2 ctrl sample for some proteins
lines(y, FullDat[i,colRep3ctrl], col = "blue") ##plot of Rep3 ctrl sample for some proteins

lines(y, FullDat[i,colRep1rnase], col = "pink")
lines(y, FullDat[i,colRep2rnase], col = "pink")
lines(y, FullDat[i,colRep3rnase], col = "pink")
}

##examples of shifts or differences in maxima; abnormalities (not normalized)
for (i in c(4148,4150:4154, 4189,4190, 4293 )){
plot(y, FullDat[i,colRep1ctrl], col = "blue", xlab = i) 
lines(y, FullDat[i,colRep2ctrl], col = "blue") 
lines(y, FullDat[i,colRep3ctrl], col = "blue") 

lines(y, FullDat[i,colRep1rnase], col = "pink")
lines(y, FullDat[i,colRep2rnase], col = "pink")
lines(y, FullDat[i,colRep3rnase], col = "pink")
}


#Normalized plots
y = 1:25

for (i in 4200:4300){
plot(y, rep1ctrlnormDataframe[i,], col = "blue", xlab = i) 
lines(y, rep2ctrlnormDataframe[i,], col = "blue") 
lines(y, rep3ctrlnormDataframe[i,], col = "blue") 

lines(y, rep1rnasenormDataframe[i,], col = "pink")
lines(y, rep2rnasenormDataframe[i,], col = "pink")
lines(y, rep3rnasenormDataframe[i,], col = "pink")
}

#Comparison normalized plot and not normalized plot

for (i in c(4150, 4000)){
plot(y, FullDat[i,colRep1ctrl], col = "blue", xlab = i) 
lines(y, FullDat[i,colRep2ctrl], col = "blue") 
lines(y, FullDat[i,colRep3ctrl], col = "blue") 

plot(y, rep1ctrlnormDataframe[i,], col = "green", xlab = i) 
lines(y, rep2ctrlnormDataframe[i,], col = "green") 
lines(y, rep3ctrlnormDataframe[i,], col = "green")

plot(y, FullDat[i,colRep1rnase], col = "pink", xlab = i)
lines(y, FullDat[i,colRep2rnase], col = "pink")
lines(y, FullDat[i,colRep3rnase], col = "pink")

plot(y, rep1rnasenormDataframe[i,], col = "orange", xlab = i)
lines(y, rep2rnasenormDataframe[i,], col = "orange")
lines(y, rep3rnasenormDataframe[i,], col = "orange")
}

plot(y, rep1ctrlnormDataframe[1,], type = "o", col = "blue"); lines(y,rep2ctrlnormDataframe[1,], col = "green"); lines(y, rep3ctrlnormDataframe[1,], col="purple")

 ## Max. for some proteins for Rep1 ctrl sample and  the fraction the maximum is in
maxRep1ctrl = apply(FullDat[1:40,colRep1ctrl],1,max)
for(i in 1:40){
    for (j in 1:150){
        if(FullDat[i,j]== maxRep1ctrl[i]){
           print(names(FullDat)[j])
        }
    }
}


```
These are some proteins that were selected from the interval of protein 4000 until protein 4300. Their maxima of the plot of the control and RNase group show differences to each other. These differences of these examples have to get examined further. These are only examples for the kind of proteins we are looking for. To further examine those we want to fuse all three curves of the replicates.Before doing that we eliminate batch effects from our data. We look for replicates with one or two NAs. When there is one NA we assign the mean of the other two values to this value and if there are two NAs we delete the third value as well.
```{r}
#batch effect free data
TripCtrldat = cbind(rep1ctrlnormData, rep2ctrlnormData, rep3ctrlnormData)
TripRnasedat = cbind(rep1rnasenormData, rep2rnasenormData, rep3rnasenormData)

tripCtrlnormdat = cbind(rep1ctrlnormDataframe, rep2ctrlnormDataframe, rep3ctrlnormDataframe)
tripRnasenormdat = cbind(rep1rnasenormDataframe, rep2rnasenormDataframe, rep3rnasenormDataframe)

tripRnasenormdat[tripRnasenormdat==0] = NA
tripCtrlnormdat[tripCtrlnormdat==0] = NA
for(i in 1:nrow(tripCtrlnormdat)){
  for (j in 1:25){
    testctrl = c(tripCtrlnormdat[i,j],tripCtrlnormdat[i,j+25], tripCtrlnormdat[i,j+50])
    if(sum(is.na(testctrl))==2) {
      cat("\n", i, j)
      tripCtrlnormdat[i, j] = NA
      tripCtrlnormdat[i, j+25] = NA
      tripCtrlnormdat[i, j+50] = NA
    }
    if(sum(is.na(testctrl))==1){
      cat("\n", i, j)
      tripCtrlnormdat[i, j] = mean(testctrl, na.rm = TRUE)
      tripCtrlnormdat[i, j+25] = mean(testctrl, na.rm = TRUE)
      tripCtrlnormdat[i, j+50] = mean(testctrl, na.rm = TRUE)
    }
  }
}

for(i in 1:nrow(tripRnasenormdat)){
  for (j in 1:25){
    testrnase = c(tripRnasenormdat[i,j],tripRnasenormdat[i,j+25], tripRnasenormdat[i,j+50])
    if(sum(is.na(testrnase))==2) {
      tripRnasenormdat[i, j] = NA
      tripRnasenormdat[i, j+25] = NA
      tripRnasenormdat[i, j+50] = NA
    }
    if(sum(is.na(testctrl))==1){
      tripRnasenormdat[i, j] = mean(testrnase, na.rm = TRUE)
      tripRnasenormdat[i, j+25] = mean(testrnase, na.rm = TRUE)
      tripRnasenormdat[i, j+50] = mean(testrnase, na.rm = TRUE)
    }
  }
}

tripRnasenormdat[is.na(tripRnasenormdat)] = 0
tripCtrlnormdat[is.na(tripCtrlnormdat)] = 0

rep1ctrlnormDataframe = tripCtrlnormdat[,1:25]
rep2ctrlnormDataframe = tripCtrlnormdat[,26:50]
rep3ctrlnormDataframe = tripCtrlnormdat[,51:75]
rep1rnasenormDataframe = tripRnasenormdat[,1:25]
rep2rnasenormDataframe = tripRnasenormdat[,26:50]
rep3rnasenormDataframe = tripRnasenormdat[,51:75]

```
There are 23 proteins that have a replicate value being a batch effect.

```{r}

#reproducibility; comparison maxima

# main maxima
fraction_abs_max = matrix(, ncol = 6, nrow = nrow(rep1ctrlnormDataframe)) 
for (i in 1:nrow(rep1ctrlnormDataframe)){
  fraction_abs_max[i,1] = which.max(rep1ctrlnormDataframe[i,])
  fraction_abs_max[i,2] = which.max(rep2ctrlnormDataframe[i,])
  fraction_abs_max[i,3] = which.max(rep3ctrlnormDataframe[i,])
  fraction_abs_max[i,4] = which.max(rep1rnasenormDataframe[i,])
  fraction_abs_max[i,5] = which.max(rep2rnasenormDataframe[i,])
  fraction_abs_max[i,6] = which.max(rep3rnasenormDataframe[i,])
}

isTRUE(all.equal(fraction_abs_max[,1], fraction_abs_max[,2], tolerance = 1.1)) 
isTRUE(all.equal(fraction_abs_max[,2], fraction_abs_max[,3], tolerance = 1.1))
isTRUE(all.equal(fraction_abs_max[,1], fraction_abs_max[,3], tolerance = 1.1)) 
isTRUE(all.equal(fraction_abs_max[,4], fraction_abs_max[,5], tolerance = 1.1))
isTRUE(all.equal(fraction_abs_max[,5], fraction_abs_max[,6], tolerance = 1.1))
isTRUE(all.equal(fraction_abs_max[,4], fraction_abs_max[,6], tolerance = 1.1))
#all TRUE

head(fraction_abs_max)

# local maxima

#local maxima 
# define local maxima: values of each of the two fractions beside the maximum are smaller than that value and the maximum contains at least 3/5/7 % of the total amount of protein


#Threshold 3
maxctrl1_3 = matrix(0, nrow=nrow(rep1ctrlnormDataframe), ncol=25)
maxctrl2_3 = matrix(0, nrow=nrow(rep1ctrlnormDataframe), ncol=25)
maxctrl3_3 = matrix(0, nrow=nrow(rep1ctrlnormDataframe), ncol=25)

for (i in 1:nrow(rep1ctrlnormDataframe)){
  
  for (j in 1){ #marginal value 1; weiterer threshold für Randwerte?
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 3 &&  rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)]){
      maxctrl1_3[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep2ctrlnormDataframe[i,j] > 3 &&  rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+1)]){
      maxctrl2_3[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep3ctrlnormDataframe[i,j] > 3 &&  rep3ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)]){
      maxctrl3_3[i,j] = j
    }
  }
  
  for(j in 2){ #marginal value 2
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 3 &&  rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+2)]){
      maxctrl1_3[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep2ctrlnormDataframe[i,j] > 3 && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-1)] &&  rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+1)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+2)]){
      maxctrl2_3[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep3ctrlnormDataframe[i,j] > 3 && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+2)]){
      maxctrl3_3[i,j] = j
    }
  }
  
  for (j in 3:23){
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 3 && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+2)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-2)]) {
      maxctrl1_3[i,j] = j
    }
    if(j != fraction_abs_max[i,2] && rep2ctrlnormDataframe[i,j] > 3 && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-1)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+1)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+2)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-2)]){
      maxctrl2_3[i,j] = j
    }
    if(j != fraction_abs_max[i,3] && rep3ctrlnormDataframe[i, j] > 3 &&  rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+2)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-2)]) {
      maxctrl3_3[i,j] = j
    }
  }
  
  
  for(j in 24){ #marginal value 3
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 3 &&  rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-2)]){
      maxctrl1_3[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep2ctrlnormDataframe[i,j] > 3 && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+1)] &&  rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-1)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-2)]){
      maxctrl2_3[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep3ctrlnormDataframe[i,j] > 3 && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-2)]){
      maxctrl3_3[i,j] = j
    }
  }
  
  for (j in 25){ #marginal value 4
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 3 &&  rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)]){
      maxctrl1_3[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep2ctrlnormDataframe[i,j] > 3 &&  rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-1)]){
      maxctrl2_3[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep3ctrlnormDataframe[i,j] > 3 &&  rep3ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)]){
      maxctrl3_3[i,j] = j
    }
  }
  
}

#Threshold 5
maxctrl1_5 = matrix(0, nrow=nrow(rep1ctrlnormDataframe), ncol=25)
maxctrl2_5 = matrix(0, nrow=nrow(rep1ctrlnormDataframe), ncol=25)
maxctrl3_5 = matrix(0, nrow=nrow(rep1ctrlnormDataframe), ncol=25)


for (i in 1:nrow(rep1ctrlnormDataframe)){
  
  for (j in 1){ #marginal value 1
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 5 &&  rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)]){
      maxctrl1_5[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep2ctrlnormDataframe[i,j] > 5 &&  rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+1)]){
      maxctrl2_5[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep3ctrlnormDataframe[i,j] > 5 &&  rep3ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)]){
      maxctrl3_5[i,j] = j
    }
  }
  
  for(j in 2){ #marginal value 2
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 5 &&  rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+2)]){
      maxctrl1_5[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep2ctrlnormDataframe[i,j] > 5 && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-1)] &&  rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+1)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+2)]){
      maxctrl2_5[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep3ctrlnormDataframe[i,j] > 5 && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+2)]){
      maxctrl3_5[i,j] = j
    }
  }
  
  for (j in 3:23){
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 5 && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+2)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-2)]) {
      maxctrl1_5[i,j] = j
    }
    if(j != fraction_abs_max[i,2] && rep2ctrlnormDataframe[i,j] > 5 && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-1)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+1)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+2)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-2)]){
      maxctrl2_5[i,j] = j
    }
    if(j != fraction_abs_max[i,3] && rep3ctrlnormDataframe[i, j] > 5 &&  rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+2)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-2)]) {
      maxctrl3_5[i,j] = j
    }
  }
  
  
  for(j in 24){ #marginal value 3
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 5 &&  rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-2)]){
      maxctrl1_5[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep2ctrlnormDataframe[i,j] > 5 && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+1)] &&  rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-1)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-2)]){
      maxctrl2_5[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep3ctrlnormDataframe[i,j] > 5 && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-2)]){
      maxctrl3_5[i,j] = j
    }
  }
  
  for (j in 25){ #marginal value 4
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 5 &&  rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)]){
      maxctrl1_5[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep2ctrlnormDataframe[i,j] > 5 &&  rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-1)]){
      maxctrl2_5[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep3ctrlnormDataframe[i,j] > 5 &&  rep3ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)]){
      maxctrl3_5[i,j] = j
    }
  }
  
}





#Threshold 7
maxctrl1_7 = matrix(0, nrow=nrow(rep1ctrlnormDataframe), ncol=25)
maxctrl2_7 = matrix(0, nrow=nrow(rep1ctrlnormDataframe), ncol=25)
maxctrl3_7 = matrix(0, nrow=nrow(rep1ctrlnormDataframe), ncol=25)

for (i in 1:nrow(rep1ctrlnormDataframe)){
  
  for (j in 1){ #marginal value 1
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 7 &&  rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)]){
      maxctrl1_7[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep2ctrlnormDataframe[i,j] > 7 &&  rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+1)]){
      maxctrl2_7[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep3ctrlnormDataframe[i,j] > 7 &&  rep3ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)]){
      maxctrl3_7[i,j] = j
    }
  }
  
  for(j in 2){ #marginal value 2
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 7 &&  rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+2)]){
      maxctrl1_7[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep2ctrlnormDataframe[i,j] > 7 && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-1)] &&  rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+1)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+2)]){
      maxctrl2_7[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep3ctrlnormDataframe[i,j] > 7 && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+2)]){
      maxctrl3_7[i,j] = j
    }
  }
  
  for (j in 3:23){
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 7 && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+2)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-2)]) {
      maxctrl1_7[i,j] = j
    }
    if(j != fraction_abs_max[i,2] && rep2ctrlnormDataframe[i,j] > 7 && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-1)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+1)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+2)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-2)]){
      maxctrl2_7[i,j] = j
    }
    if(j != fraction_abs_max[i,3] && rep3ctrlnormDataframe[i, j] > 7 &&  rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+2)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-2)]) {
      maxctrl3_7[i,j] = j
    }
  }
  
  
  for(j in 24){ #marginal value 3
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 7 &&  rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j+1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)] && rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-2)]){
      maxctrl1_7[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep2ctrlnormDataframe[i,j] > 7 && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j+1)] &&  rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-1)] && rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-2)]){
      maxctrl2_7[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep3ctrlnormDataframe[i,j] > 7 && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j+1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-1)] && rep3ctrlnormDataframe[i,j] > rep3ctrlnormDataframe[i, (j-2)]){
      maxctrl3_7[i,j] = j
    }
  }
  
  for (j in 25){ #marginal value 4
    if(j != fraction_abs_max[i,1] && rep1ctrlnormDataframe[i,j] > 7 &&  rep1ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)]){
      maxctrl1_7[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep2ctrlnormDataframe[i,j] > 7 &&  rep2ctrlnormDataframe[i,j] > rep2ctrlnormDataframe[i, (j-1)]){
      maxctrl2_7[i,j] = j
    }
    if(j != fraction_abs_max[i,1] && rep3ctrlnormDataframe[i,j] > 7 &&  rep3ctrlnormDataframe[i,j] > rep1ctrlnormDataframe[i, (j-1)]){
      maxctrl3_7[i,j] = j
    }
  }
  
}

 
# Jetzt muss man noch vergleichen wie viele man dann rausschmeißt


# three datasets of 0 but with values at places where there is a maximum
# comparison


compare_max = function(a,b){
logf = matrix(FALSE, ncol = 25, nrow = 7081)
for (i in 1:7081){
  for (j in 2:24){
    if(a[i,j]==b[i,j]){}
      else if(b[i,(j+1)] != 0 || b[i,(j-1)] != 0){}
      else {logf[i,j] = TRUE}
    }
}
return(sum(logf))
}


#Comparison thresholds
compare_max(maxctrl1_3,maxctrl2_3) 
compare_max(maxctrl1_3,maxctrl3_3)
compare_max(maxctrl2_3,maxctrl3_3) 

compare_max(maxctrl1_5,maxctrl2_5) 
compare_max(maxctrl1_5,maxctrl3_5) 
compare_max(maxctrl2_5,maxctrl3_5) 

compare_max(maxctrl1_7,maxctrl2_7)
compare_max(maxctrl1_7,maxctrl3_7) 
compare_max(maxctrl2_7,maxctrl3_7) 




##


isTRUE(all.equal(maxctrl1_3,maxctrl2_3, tolerance = 1.1))
isTRUE(all.equal(maxctrl1_3,maxctrl3_3, tolerance = 1.1))
isTRUE(all.equal(maxctrl2_3,maxctrl3_3, tolerance = 1.1))

isTRUE(all.equal(maxctrl1_5,maxctrl2_5, tolerance = 1.1))
isTRUE(all.equal(maxctrl1_5,maxctrl3_5, tolerance = 1.1))
isTRUE(all.equal(maxctrl2_5,maxctrl3_5, tolerance = 1.1))

isTRUE(all.equal(maxctrl1_7,maxctrl2_7, tolerance = 1.1))
isTRUE(all.equal(maxctrl1_7,maxctrl3_7, tolerance = 1.1))
isTRUE(all.equal(maxctrl2_7,maxctrl3_7, tolerance = 1.1))

##all FALSE so there are shifts



```

```{r}
#mean of control replicates of all proteins  
meanRepctrl = matrix(nrow= nrow(tripCtrlnormdat), ncol = 25)
for (j in 1:nrow(tripCtrlnormdat)){ 
  for (i in 1:25){
    meanRepctrl[j,i] = (rep1ctrlnormDataframe[j,i] + rep2ctrlnormDataframe[j,i] + rep3ctrlnormDataframe[j,i])/3}}

#mean of rnase replicates of all proteins 
meanRepRNase = matrix(nrow= nrow(FullDat), ncol = 25)
for (j in 1:nrow(tripCtrlnormdat)){ 
  for (i in 1:25){
    meanRepRNase[j,i] = (rep1rnasenormDataframe[j,i] + rep2rnasenormDataframe[j,i] + rep3rnasenormDataframe[j,i])/3}}





