---
title: "RDeep HeLa Interphase Analysis"
author: "Laura Herrfurth"
date: "8 5 2022"
output: html_document
---

```{r}
#Load data RDeep_HeLa_Interphase 
FullData = read.table("C:/Users/Laura Herrfurth/Documents/Data Analysis Projekt/RDeeP_HeLa_Interphase.csv",header = TRUE, row.names = 1, sep = ";")


#First survey
head(FullData)
summary(FullData)
dim(FullData)
colnames(FullData)
rownames(FullData)

sapply(FullData,mode)
sapply(FullData,class)

sum(sapply(FullData[,2], is.numeric)) 



```

The data contains 7086 proteins and 25 fractions which were each repeated three times as a control sample and three times with RNase.

After the first survey we have to find a way to deal with the missing values in the data.The options are to remove rows (proteins) with a very high count or to replace all missing values with the mean of the general count of a specific protein of the control or the RNase sample. We will delete row with all zeros and with all zeros in either all Ctrl replicates or in all RNase replicates.


```{r}

# missing values have the value 0; delete these values -> NA
which(FullData == 0)
data_rm = FullData[-which(FullData == 0),] #deleted complete rows!
dim(data_rm) #huge number of zeros!

#Reduce data set into smaller data sets 
colRep1ctrl = seq(1, 150, 6) ##all columns with rep1 ctrl 
colRep2ctrl = seq(2, 150, 6) ##all columns with rep2 ctrl 
colRep3ctrl = seq(3, 150, 6) ##all columns with rep3 ctrl 

colRep1RNAse = seq(4, 150, 6) ##all columns with rep1 RNAse 
colRep2RNAse = seq(5, 150, 6) ##all columns with rep2 RNAse 
colRep3RNAse = seq(6, 150, 6) ##all columns with rep3 RNAse 

# delete rows with only zeros or proteins with only zeros in the Ctrl or RNase samples
a = which(rowSums(FullData==0)==150)
b = which(rowSums(FullData[,c(colRep1ctrl, colRep2ctrl, colRep3ctrl)]== 0) ==75)
c = which(rowSums(FullData[,c(colRep1RNAse, colRep2RNAse, colRep3RNAse)]== 0) ==75)


FullData = FullData[-c(2089,2993, 4123,4405, 6216),]


# data sets for each replicate; normalization 
rep1ctrlnormData = t(apply(FullData[, colRep1ctrl], 1, function(x) x/(sum(x)/100)))
rep2ctrlnormData = t(apply(FullData[, colRep2ctrl], 1, function(x) x/(sum(x)/100)))
rep3ctrlnormData = t(apply(FullData[, colRep3ctrl], 1, function(x) x/(sum(x)/100)))
rep1rnasenormData = t(apply(FullData[, colRep1rnase], 1, function(x) x/(sum(x)/100)))
rep2rnasenormData = t(apply(FullData[, colRep2rnase], 1, function(x) x/(sum(x)/100)))
rep3rnasenormData = t(apply(FullData[, colRep3rnase], 1, function(x) x/(sum(x)/100)))

rep1ctrlnormDataframe = as.data.frame(rep1ctrlnormData)
rep2ctrlnormDataframe = as.data.frame(rep2ctrlnormData)
rep3ctrlnormDataframe = as.data.frame(rep3ctrlnormData)
rep1rnasenormDataframe = as.data.frame(rep1rnasenormData)
rep2rnasenormDataframe = as.data.frame(rep2rnasenormData)
rep3rnasenormDataframe = as.data.frame(rep3rnasenormData)


sum(rep1ctrlnormData[1,]) # == 100


#mean of replicates of first column 
meanRepctrl = vector()
for (i in 1:25){
  meanRepctrl[i] = (rep1ctrlnormData[1,i] + rep2ctrlnormData[1,i] + rep3ctrlnormData[1,i])/3}

meanRepRNase = vector()
for (i in 1:25){
  meanRepRNase[i] = (rep1rnasenormData[1,i] + rep2rnasenormData[1,i] + rep3rnasenormData[1,i])/3}


#Mean aller Reps aller Zeilen berechnen ?? 
##Um Plots der Reps zu fusionieren
#Gibt nur leeren Datensatz
u = vector()
for (i in nrow(FullData)){
  for (j in 1:25){
    u[i,j] = as.data.frame((rep1ctrlnormDataframe[i,j] + rep2ctrlnormDataframe[i,j] + rep3ctrlnormDataframe[i,j])/3)
  }
}

```
After deleting proteins we have to examine differences in the different samples and to illustrate them. That's why we normalized our data to compare the different replicates.We normalized the amount of one replicate to 100 to be able to assign protein amounts to percentages/relations. We are looking at the plots of single proteins and compare the lines and maxima of the control and the RNase group. 

```{r}
#Plots for fractions of each gene
#not normalized
for (i in 4200:4300){
plot(y, FullData[i,colRep1ctrl], col = "blue", xlab = i) ##plot of Rep1 ctrl sample for some proteins
lines(y, FullData[i,colRep2ctrl], col = "blue") ##plot of Rep2 ctrl sample for some proteins
lines(y, FullData[i,colRep3ctrl], col = "blue") ##plot of Rep3 ctrl sample for some proteins

lines(y, FullData[i,colRep1rnase], col = "pink")
lines(y, FullData[i,colRep2rnase], col = "pink")
lines(y, FullData[i,colRep3rnase], col = "pink")
}

##examples of shifts or differences in maxima; abnormalities (not normalized)
for (i in c(4148,4150:4154, 4189,4190, 4293 )){
plot(y, FullData[i,colRep1ctrl], col = "blue", xlab = i) 
lines(y, FullData[i,colRep2ctrl], col = "blue") 
lines(y, FullData[i,colRep3ctrl], col = "blue") 

lines(y, FullData[i,colRep1rnase], col = "pink")
lines(y, FullData[i,colRep2rnase], col = "pink")
lines(y, FullData[i,colRep3rnase], col = "pink")
}


#Normalized plots
y = 1:25

for (i in 4200:4300){
plot(y, rep1ctrlnormDataframe[i,], col = "blue", xlab = i) 
lines(y, rep2ctrlnormDataframe[i,], col = "blue") 
lines(y, rep3ctrlnormDataframe[i,], col = "blue") 

lines(y, rep1rnasenormDataframe[i,], col = "pink")
lines(y, rep2rnasenormDataframe[i,], col = "pink")
lines(y, rep3rnasenormDataframe[i,], col = "pink")
}

#Comparison normalized plot and not normalized plot
## 
for (i in c(4150, 4000)){
plot(y, FullData[i,colRep1ctrl], col = "blue", xlab = i) 
lines(y, FullData[i,colRep2ctrl], col = "blue") 
lines(y, FullData[i,colRep3ctrl], col = "blue") 

plot(y, rep1ctrlnormDataframe[i,], col = "green", xlab = i) 
lines(y, rep2ctrlnormDataframe[i,], col = "green") 
lines(y, rep3ctrlnormDataframe[i,], col = "green")

plot(y, FullData[i,colRep1rnase], col = "pink", xlab = i)
lines(y, FullData[i,colRep2rnase], col = "pink")
lines(y, FullData[i,colRep3rnase], col = "pink")

plot(y, rep1rnasenormDataframe[i,], col = "orange", xlab = i)
lines(y, rep2rnasenormDataframe[i,], col = "orange")
lines(y, rep3rnasenormDataframe[i,], col = "orange")
}
## Bei 4000 shift zwischen normalisiert und nicht normalisiert?! Etwas falsch gemacht? Aber bei 4150 stimmt polt überein! Bedeutung?


 ## Max. for some proteins for Rep1 ctrl sample and  the fraction the maximum is in
maxRep1ctrl = apply(FullData[1:40,colRep1ctrl],1,max)
for(i in 1:40){
    for (j in 1:150){
        if(FullData[i,j]== maxRep1ctrl[i]){
           print(names(FullData)[j])
        }
    }
}


```
These are some proteins that were selected from the interval of protein 4000 until protein 4300. Their maxima of the plot of the control and RNase group show differences to each other. These differences of these examples have to get examined further. These are only examples for the kind of proteins we are looking for. To further examine those we want to fuse all three curves of the replicates.
```{r}




```